\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-15 arch.tex
added a new figure to illustrate planning window of a reactor and how it relates to reactor latency and look-ahead

\comment{this might be a subsubsection before someplace since it
  introduces the concept of latency/lookahead.}
These events could potentially produce new flaws to be resolved while
any single deliberation step will likely reduce the number of flaws
for resolution. The scope of planning for a reactor also plays a role
in the deliberation process as we limit deliberation to the sliding
temporal window $[\tau+\lambda, \tau+\lambda+\pi]$ \cite{py10} where:

@@

\comment{Insert a figure here [AAMAS?] showing $\pi \lambda$} Such a
scope allows filtering of tokens that are either necessarily ending
before $\tau$ or necessarily starting after, focusing the planning
problem on only those tokens that are within a ``reasonable''
future. This window is taken into account by the \rx agent which will
notify a reactor of new {\em internal} goals not only when they
overlap this reactor specific window but also for the deliberation
solver in order to reduce the number of tokens to be evaluated to
reduce deliberation cost and performance. As time advances flaws that
were initially beyond this temporal horizon will become active which a
reactor can evaluate. This results in an apparent \emph{continuous
  planning} of the reactor. When there are no more flaws present in
the current planning scope a partial plan solution is found. This has
two effects:

>>>>

\comment{this might be a subsubsection before someplace since it
  introduces the concept of latency/lookahead. TODO: yep it needs to
  move up to the architecture section.}
These events could potentially produce new flaws to be resolved while
any single deliberation step will likely reduce the number of flaws
for resolution. The scope of planning for a reactor also plays a role
in the deliberation process as we limit deliberation to the sliding
temporal window $[\tau+\lambda, \tau+\lambda+\pi]$ \cite{py10} where:

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.65\columnwidth]{figs/plan_window}
  \caption{The planning window of the deliberation solver and its
    relation with the reactor latency and look-ahead. The dark grey tokens
    with dashed borders are excluded from deliberation as they do not
    overlap the interval $[\tau, \tau+\lambda+\pi]$}
  \label{fig:plan:window}
\end{figure}

As Fig. \ref{fig:plan:window} illustrates,  such a
scope allows filtering of tokens that are either necessarily ending
before $\tau$ or necessarily starting after, focusing the planning
problem on only those tokens that are within a ``reasonable''
future. This window is taken into account by the \rx agent which will
notify a reactor of new {\em internal} goals not only when they
overlap this reactor specific window but also for the deliberation
solver in order to reduce the number of tokens to be evaluated to
reduce deliberation cost and performance. As time advances flaws that
were initially beyond this temporal horizon will become active which a
reactor can evaluate. This results in an apparent \emph{continuous
  planning} of the reactor. When there are no more flaws present in
the current planning scope a partial plan solution is found. This has
two effects:
